Energy and the CES production function

### 2015-08-21 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Fixed raw CES table.

data_CES_sigma_raw <- sigma_data %>% select(Country, Model, flavor, Energy, Nest, CSP, sigma_1, sigma)
data_CES_sigma_raw <- plyr::rename(data_CES_sigma_raw, c("sigma" = "$\\sigma$",
                                                         "sigma_1" = "$\\sigma_1$"))
data_CES_sigma_raw <- plyr::rename(data_CES_sigma_raw, c("flavor" = "Factors of prod."))
data_CES_sigma_raw$CSP <- plyr::mapvalues(data_CES_sigma_raw$CSP, 
                                         from=c("Adhere to CSP", "Reject CSP"), 
                                         to=c("Adhere", "Reject"))
data_CES_sigma_raw$Energy <- plyr::mapvalues(data_CES_sigma_raw$Energy, 
                                         from=c("Without energy", "With energy"), 
                                         to=c("Without", "With"))

>>>>

# data_CES_sigma_raw <- sigma_data %>% select(Country, Model, flavor, Energy, Nest, CSP, sigma_1, sigma)
# data_CES_sigma_raw <- plyr::rename(data_CES_sigma_raw, c("sigma" = "$\\sigma$",
#                                                          "sigma_1" = "$\\sigma_1$"))
# data_CES_sigma_raw <- plyr::rename(data_CES_sigma_raw, c("flavor" = "Factors of prod."))
# data_CES_sigma_raw$CSP <- plyr::mapvalues(data_CES_sigma_raw$CSP, 
#                                          from=c("Adhere to CSP", "Reject CSP"), 
#                                          to=c("Adhere", "Reject"))
# data_CES_sigma_raw$Energy <- plyr::mapvalues(data_CES_sigma_raw$Energy, 
#                                          from=c("Without energy", "With energy"), 
#                                          to=c("Without", "With"))

data_CES_sigma_raw <- AllCoeffs %>%
  filter(model=="CES") %>%
   mutate(
     Nest = plyr::mapvalues(nest,
                            from=c("kl", "kle", "lek", "ekl"),
                            to=c("$kl$", "$(kl)e$", "$(le)k$", "$(ek)l$")),
     CSP = plyr::mapvalues(CSP, 
                           from=c("Adhere to CSP", "Reject CSP"), 
                           to=c("Adhere", "Reject")),
     Energy = plyr::mapvalues(energy, 
                              from=c("Without energy", "With energy"), 
                              to=c("Without", "With"))
     ) %>%
  select(Country, flavor, Energy, Nest, CSP, sigma_1, sigma) %>%
  plyr::rename(
    c("sigma" = "$\\sigma$",
      "sigma_1" = "$\\sigma_1$",
      "flavor" = "Factors of Prod."))
